No need to know: astrophysics-free gravitational-wave cosmology

### 2024-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Biases observed in parametric models}
\label{ap:parametric bias}
\new{Figure~\ref{fig:parametric bias} shows recovered posteriors on \Ho{} as inferred from 50 mock catalogs using both the \bpl{} and \plp{} parametric models.
We find that the \plp{} model recovers \Ho{} posteriors that are largely symmetric about the true value, whereas the \bpl{} model typically finds more support for larger \Ho{} values.
We note that \citep{pierra_study_2023} report an underestimate of \Ho{} with a fit of their Broken Power Law model to a single dataset generated with \plp, but their prior bounds on the maximum mass parameter do not extend below the injected value of that parameter, which in turn does not allow for the possibility of an overestimated \Ho{}.

Regardless, this systematic offset further demonstrates that incorrect parametric models induce a systematic bias in cosmological inference rather than an increased statistical uncertainty. 
Other parametric models may show different trends depending on which parts of the mass distribution they incorrectly model and how.
Therefore, while we are able to identify the shortcomings of \bpl{} when \plp{} describes the true mass distribution, it is not possible in practice to know which direction an incorrect parametric model will bias \Ho{}.
Mitigating the bias by using more flexible models may thus be the simplest solution to this problem.}

>>>>

\section{Biases observed in parametric models}
\label{ap:parametric bias}
\new{Figure~\ref{fig:parametric bias} shows recovered posteriors on \Ho{} as inferred from 50 mock catalogs using both the \bpl{} and \plp{} parametric models.
We find that the \plp{} model recovers \Ho{} posteriors that are largely symmetric about the true value, whereas the \bpl{} model typically finds more support for larger \Ho{} values.
We note that \citep{pierra_study_2023} report an underestimate of \Ho{} with a fit of their Broken Power Law model to a single dataset generated with \plp, but their prior bounds on the maximum mass parameter do not extend below the injected value of that parameter, which in turn does not allow for the possibility of an overestimated \Ho{}.}

\new{Regardless, this systematic offset further demonstrates that incorrect parametric models induce a systematic bias in cosmological inference rather than an increased statistical uncertainty. 
Other parametric models may show different trends depending on which parts of the mass distribution they incorrectly model and how.
Therefore, while we are able to identify the shortcomings of \bpl{} when \plp{} describes the true mass distribution, it is not possible in practice to know which direction an incorrect parametric model will bias \Ho{}.
Mitigating the bias by using more flexible models may thus be the simplest solution to this problem.}
